Total Amount of Vaccinations Among Black population in the Target Zip Codes

### 2023-05-05 code/analysis_code/statisticalanalysis.qmd
Auto stash before merge of "master" and "origin/master"

### Library
```{r}
library(tidymodels)
library(vip) #most important variables in LASSO Model
library(forcats)
library(tidyverse)
library(Metrics) #RMSE
library(rsq) #rsqured 
library(yardstick)
library(MASS) #used for AIC forward selection 
library(glmnet) #for ridge regression 
```

@@

>>>>

### Library
```{r}
library(tidymodels)
library(vip) #most important variables in LASSO Model
library(forcats)
library(tidyverse)
library(Metrics) #RMSE
library(rsq) #rsqured 
library(yardstick)
library(MASS) #used for AIC forward selection 
library(glmnet) #for ridge regression 
library(here)
```

@@

### Bivariate Analysis Through Linear Regression

```{r}
# fit linear model 
lm_mod <- linear_reg()

#fit model with total rate difference as outcome and total vax rate as predictor
total_rate_fit <- lm_mod %>% 
  fit( TOTAL_RATE_DIFF ~ TOTAL_VAX_RATE,
      data = combined) 
total_rate <- tidy(total_rate_fit) 
print(total_rate)

#Save Linear Regression Output Table
table1= here("results", "table1.RDS")
saveRDS(total_rate, file = table1) 
```

```{r}
#fit model with total rate difference as outcome and male vax rate as predictor
Male_rate_fit <- lm_mod %>% 
  fit( TOTAL_RATE_DIFF ~ Male_VAX_RATE,
      data = combined) 
Male_rate <- tidy(Male_rate_fit) 
print(Male_rate)

#Save Linear Regression Output Table
table2= here("results", "table2.RDS")
saveRDS(Male_rate, file = table2) 
```

```{r}
#fit model with total rate difference as outcome and female vax rate as predictor
Female_rate_fit <- lm_mod %>% 
  fit( TOTAL_RATE_DIFF ~ Female_VAX_RATE,
      data = combined) 
Female_rate <- tidy(Female_rate_fit) 
print(Female_rate)

#Save Linear Regression Output Table
table3= here("results", "table3.RDS")
saveRDS(Female_rate, file = table3) 
```

```{r}
#fit model with total rate difference as outcome and Age_05_09_VAX_RATE as predictor
Age_05_09_rate_fit <- lm_mod %>% 
  fit( TOTAL_RATE_DIFF ~ Age_05_09_VAX_RATE,
      data = combined) 
Age_05_09_rate <- tidy(Age_05_09_rate_fit) 
print(Age_05_09_rate)

#Save Linear Regression Output Table
table4= here("results", "table4.RDS")
saveRDS(Age_05_09_rate, file = table4) 
```

```{r}
#fit model with total rate difference as outcome and Age_10_17_VAX_RATE as predictor
Age_10_17_rate_fit <- lm_mod %>% 
  fit( TOTAL_RATE_DIFF ~ Age_10_17_VAX_RATE,
      data = combined) 
Age_10_17_rate <- tidy(Age_10_17_rate_fit) 
print(Age_10_17_rate)

#Save Linear Regression Output Table
table5= here("results", "table5.RDS")
saveRDS(Age_10_17_rate, file = table5) 
```

```{r}
#fit model with total rate difference as outcome and Age_18_44_VAX_ as predictor
Age_18_44_rate_fit <- lm_mod %>% 
  fit( TOTAL_RATE_DIFF ~ Age_18_44_VAX_RATE,
      data = combined) 
Age_18_44_rate <- tidy(Age_18_44_rate_fit) 
print(Age_18_44_rate)

#Save Linear Regression Output Table
table6= here("results", "table6.RDS")
saveRDS(Age_18_44_rate, file = table6) 
```

```{r}
#fit model with total rate difference as outcome and Age_45_64_VAX_RATE as predictor
Age_45_64_rate_fit <- lm_mod %>% 
  fit( TOTAL_RATE_DIFF ~ Age_45_64_VAX_RATE,
      data = combined) 
Age_45_64_rate <- tidy(Age_45_64_rate_fit) 
print(Age_45_64_rate)

#Save Linear Regression Output Table
table7= here("results", "table7.RDS")
saveRDS(Age_45_64_rate, file = table7) 
```

```{r}
#fit model with total rate difference as outcome and Age_65Plus_VAX_RATE as predictor
Age_65Plus_rate_fit <- lm_mod %>% 
  fit( TOTAL_RATE_DIFF ~ Age_65Plus_VAX_RATE,
      data = combined) 
Age_65Plus_rate <- tidy(Age_65Plus_rate_fit) 
print(Age_65Plus_rate)

#Save Linear Regression Output Table
table8= here("results", "table8.RDS")
saveRDS(Age_65Plus_rate, file = table8) 
```

```{r}
#fit model with total rate difference as outcome and Interventione as predictor
Intervention_fit <- lm_mod %>% 
  fit( TOTAL_RATE_DIFF ~ Intervention,
      data = combined) 
Intervention <- tidy(Intervention_fit) 
print(Intervention)

#Save Linear Regression Output Table
table9= here("results", "table9.RDS")
saveRDS(Intervention, file = table9) 
```
